Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-05 measurements.tex
Some updates

\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.3\textwidth]{images/rasp1_good_vs_g_enc_gf2.pdf}
        \caption[]%
        {{\small $q = 2$}}    
        \label{fig:mean and std of net14}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}  
        \centering 
        \includegraphics[width=\textwidth]{images/rasp1_good_vs_g_enc_gf256.pdf}
        \caption[]%
        {{\small $q = 2^8$}}    
        \label{fig:mean and std of net24}
    \end{subfigure}
    \vskip\baselineskip
    \begin{subfigure}[b]{0.475\textwidth}   
        \centering 
        \includegraphics[width=\textwidth]{images/rasp1_good_vs_B_enc_gf2.pdf}
        \caption[]%
        {{\small $q = 2$}}    
        \label{fig:mean and std of net34}
    \end{subfigure}
    \quad
    \begin{subfigure}[b]{0.475\textwidth}   
        \centering 
        \includegraphics[width=\textwidth]{images/rasp1_good_vs_B_enc_gf256.pdf}
        \caption[]%
        {{\small $q = 2^8$}}    
        \label{fig:mean and std of net44}
    \end{subfigure}
    \caption[ The average and standard deviation of critical parameters ]
    {\small The average and standard deviation of critical parameters: Region R4} 
    \label{fig:mean and std of nets}
\end{figure*}

>>>>

\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=1.2\textwidth]{images/rasp1_good_vs_g_enc_gf2.pdf}
        \caption[]%
        {{\small $q = 2$}}    
        \label{fig:mean and std of net14}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}  
        \centering 
        \includegraphics[width=1.2\textwidth]{images/rasp1_good_vs_g_enc_gf256.pdf}
        \caption[]%
        {{\small $q = 2^8$}}    
        \label{fig:mean and std of net24}
    \end{subfigure}
    \vskip\baselineskip
    \begin{subfigure}[b]{0.475\textwidth}   
        \centering 
        \includegraphics[width=1.2\textwidth]{images/rasp1_good_vs_B_enc_gf2.pdf}
        \caption[]%
        {{\small $q = 2$}}    
        \label{fig:mean and std of net34}
    \end{subfigure}
    \quad
    \begin{subfigure}[b]{0.475\textwidth}   
        \centering 
        \includegraphics[width=1.2\textwidth]{images/rasp1_good_vs_B_enc_gf256.pdf}
        \caption[]%
        {{\small $q = 2^8$}}    
        \label{fig:mean and std of net44}
    \end{subfigure}
    \caption[ The average and standard deviation of critical parameters ]
    {\small Encoder goodput measurements for the \ac{Raspi} 1} 
    \label{fig:mean and std of nets}
\end{figure*}
